Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-02-06 Documents/Euler/Benchmarks1D/draft.tex
Removed a few packages
fixes for compilation

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage{times}
\usepackage{url}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{yhmath}
\usepackage{natbib}
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}
\usepackage{graphicx}
\graphicspath{ {figures/} }

>>>>

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{cite}
%\usepackage{times}
\usepackage{url}
%\usepackage{hyperref}
\usepackage{natbib}
%\hypersetup{
 % bookmarksnumbered = true,
  %bookmarksopen=false,
  %pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  %pdffitwindow=true,      % window fit to page when opened
  %pdfnewwindow=true, % links in new window
  %colorlinks=true,           % false: boxed links; true: colored links
  %linkcolor=blue,            % color of internal links
  %citecolor=magenta,    % color of links to bibliography
  %filecolor=magenta,     % color of file links
  %urlcolor=cyan              % color of external links
%}
\usepackage{graphicx}
\graphicspath{ {figures/} }
